%-------------------------
% Resume in Latex
% Author : Kyuhwan Lee
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------
\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

%----------FONT OPTIONS----------
\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge \scshape Kyuhwan Lee} \\ \vspace{1pt}
    \small 765-637-1584 $|$ \href{mailto:x@x.com}{\underline{lee3669@purdue.edu}} $|$ 
    \href{https://linkedin.com/in/...}{\underline{linkedin.com/in/kyuhwanl}} $|$
    \href{https://github.com/...}{\underline{github.com/kyuhwan720}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Purdue University}{West Lafayette, IN}
      {B.S - Computer Engineering Tech, Minor in CIT}{Aug. 2020 -- May 2026}
  \resumeSubHeadingListEnd

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Cloud Security Engineer, Intern}{June 2022 -- Aug. 2022}
      {ShinwooTNS}{Seoul, South Korea}
      \resumeItemListStart
        \resumeItem{Performed threat analysis in a 24/7 environment, gaining 99\% security in data.}
        \resumeItem{Managed and created rules and policies for 5,000 end-users in the data protection area.}
        \resumeItem{Successfully secured and monitored 5 websites with 0 major attacks.}
        \resumeItem{Increased customer satisfaction ratings by 30\% by mapping new software features.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Assistant Bartender}{May 2022 -- June 2022}
      {OB Bear Pub}{Seoul, South Korea}
      \resumeItemListStart
        \resumeItem{Assisted in the preparation and serving of drinks and food, ensuring customer satisfaction.}
        \resumeItem{Demonstrated strong multitasking skills, efficiently handling both cleaning responsibilities and serving duties.}
      \resumeItemListEnd
      
    \resumeSubheading
      {Undergraduate Teaching Assistant}{Jan. 2022 -- May 2022}
      {Purdue University}{West Lafayette, IN}
      \resumeItemListStart
          \resumeItem{Lab assistant for Data Acquisition and Systems Control class.}
        \resumeItem{Guided 40+ students in understanding complex technical concepts.}
        \resumeItem{Managed and maintained lab equipment worth \$15K, ensuring proper functionality.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
    
      \resumeProjectHeading
          {\textbf{Autonomous Vehicle} $|$ \emph{C++, VHDL, MATLAB}}{Jan. 2023 -- May 2023}
          \resumeItemListStart
            \resumeItem{Designed a Model Predictive Control system to utilize a mathematical model of the vehicle's dynamics.}
            \resumeItem{Implemented control algorithms and steering angle adjustment strategies to track vehicle's trajectory.}
            \resumeItem{Developed an application to identify impending rollover scenarios and initiate targeted brake interventions.}
          \resumeItemListEnd
          
      \resumeProjectHeading
          {\textbf{PER22} $|$ \emph{C, Python, Docker, Git}}{Aug. 2022 -- Apr. 2023}
          \resumeItemListStart
            \resumeItem{Developed a PyQt application used to modify tracked variables and display live data on the car.}
            \resumeItem{Designed an LCD dashboard with simple UI and basic page turning.}
            \resumeItem{Supported creation of program to calculate weight transfer for finding optimal sprocket ratio.}
          \resumeItemListEnd
          
        \resumeProjectHeading
          {\textbf{AD LDAP Test Environment} $|$ \emph{Cato SASE Cloud, Node.js}}{June 2022 -- Present}
          \resumeItemListStart
              \resumeItem{Created LDAP protocol server in Node.js to configure automatic user provisioning.}
            \resumeItem{Configured custom IP, Subnet mask, Default Gateway, and DNS Server Address.}
            \resumeItem{Achieved improved user synchronization resulting in enhanced system integration and user management.}
            \resumeItem{Generated comprehensive test plans utilizing JMeter and Wireshark to validate the functionality.}
          \resumeItemListEnd
          
        \resumeProjectHeading
          {\textbf{Icarus} $|$ \emph{C++, Git}}{Aug. 2021 -- May 2022}
          \resumeItemListStart
            \resumeItem{Implemented communication interface between the altimeter and computer for real-time data exchange.}
            \resumeItem{Developed parachute deploying mechanism on predetermined altitude thresholds.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL, JavaScript, HTML/CSS, Ruby, VHDL, Verilog, MATLAB, R} \\
     \textbf{Technologies}{: Git, React, Node.js, Quartus II, Docker, Linux, Windows Server, Microsoft Access} 
    }}
 \end{itemize}
 
%-------------------------------------------
\end{document}
